\documentclass[11pt]{res} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document} 
 
\name{DENNIS R. GLITCH\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf PRESENT ADDRESS}\\ Rattanai Sawaspanich\\
Oregon State University	\\
2003 McNary Complex	\\
Corvallis, Oregon 97331-1407	\\
(541) 206-0686\\}

\address{{\bf PERMANENT ADDRESS} \\24/3-7 Rayonghighway No.3191\\Maptaput, Muang, Rayong\\Thailand  21150\\(+66)38 691-688}
                                             
\begin{resume}
                                               
\section{STRENGTHS / SKILLS}
\begin {itemize}
\item Experience in computer programming and maintenance -- knowledge of Visual Basic, C/C++ and HTML.
\item Assemble, maintain, and change any computer components from hardware to software including OS installation (Microsoft window).
\item Expert in Microsoft Excel -- creating macro, organizing data, conditioning cell format, etc.
\item Familiar with Microsoft Access and used to be able to create a data base system by combining Visual Basic and MS Access together.
\item Strong work ethic - full time employee during summer for auto-mechanic.
\item Ability to learn quickly and independently -- I taught myself English.
\end{itemize}

 
\section{EDUCATION} 
 \noindent Oregon State University, Corvallis, OR\\
Bachelor of Science: Electrical and Computer Engineering\\
Expected graduation: June 2016\\

 
\section{EXPERIENCE} 
 AUTO MECHANIC ASSISTANT \\
Maptaput, Muang, Rayong, Thailand \\
Summer 2012
\vspace{0.2in}
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Met with customers and answered their questions, explaining technical terms in a way they could understand. 
   \item Chaged oil filter, car fluids, headlights, windshield wipers, and assembled basic parts.
  \item  Worked with six others mechanics to fix and maintain automobiles efficiently and thoroughly.
 \end{itemize}

TEACHER ASSISTANT\\
Computer lab, Rayongwittayakom High School, Thailand \\ 
2007 - 2010
\vspace{0.2in}
 \begin{itemize} \itemsep -2pt
   \item Assisted in the computer labs for programming classes.
  \item Tutored small groups of students to get them ready for quizzes and exams.
  \item Worked with people from different backgrounds using various approaches to reach the same practical method of program debugging.
\end{itemize} 

\section{HONORS} 
\begin{itemize}
\item  Highest Score in AP Physic class 2011, Henry D. Sheldon High School, Eugene, OR.
\item  Top 15\% of graduated class 2012, Marist Cathoric High School, Eugene, OR.
\end{itemize}
 
\section{ACTIVITIES} 
 \begin{itemize}
\item Nation Honor Society, 2010-2012
\item Swim team, 2010
\item An AFS exchange student, 2010
\item Sheldon High School Chess team, 3rd board , 2011
\item Maristh Catholic High School Chess team, 1st board, 2012
\end{itemize}

 
\section{HOBBIES} 
 
PC gaming, Making indiviual electronic project,Chess, Settler of Catan,  Badminton.
 

\end{resume}
\end{document}











